Energy and the CES production function

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Eliminated stringsAsFactors=FALSE. Was unnecessary.

    # return this.  ### No need to name and store it.
    melt(
      trimmed_historical_data, 
      measure.vars = measure.vars, 
      value.name = "value",
      variable.name = "variable") %>%
    mutate(
      Country = Country,
      flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted"),
      variable = as.character(variable, stringsAsFactors=FALSE) # eliminate factors which cause warnings with bind_rows() below.
      )
  }
  ) %>%

>>>>

    # return this.  ### No need to name and store it.
    melt(
      trimmed_historical_data, 
      measure.vars = measure.vars, 
      value.name = "value",
      variable.name = "variable") %>%
    mutate(
      Country = Country,
      flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted"),
      variable = as.character(variable) # eliminate factors, which cause warnings with bind_rows() below.
      )
  }
  ) %>%
